Synthesis of Linear Functional Programs

### 2021-05-09 article/article.tex
some evaluation

The full and partial synthesis mentioned are closely related, in which the latter is also a complete synthesis, but inserted inside another, bigger, program that makes use the synthetized function.

@@

>>>>

The full and partial synthesis mentioned are closely related, in which the latter is also a complete synthesis, but inserted inside another, bigger, program that makes use pf the synthetized function.

@@

\mypara{Evaluation}
Validation and evaluation of our work is fairly simple. Simple questions such as \emph{does it typecheck}? \emph{can you synth}? \emph{how fast}?
are the core of our evaluation. In more concrete terms, we can compare our times to state of the art synthetizers, present a list of working examples
of programs synthesed by our synth, and according benchmarks. On the eventual addition of recursive functions, refinement types, and interactive synthesis,
we'll consider, respectively, other examples to showcase recursive functions synthesis, updated times for benchmarks with refinement types, and a display of
the possible user interaction in the user process, and the resulting function following it.
